% Copyright (c) 2015 Luke Bowden and Callum O'Brien 

% Permission is granted to copy, distribute and/or modify this document under 
% the terms of the GNU Free Documentation License, Version 1.3 or any later 
% version published by the Free Software Foundation; with no Invariant Sections,
% no Front-Cover Texts, and no Back-Cover Texts. A copy of the license is 
% included in the file entitled "LICENSE.md".

\documentclass[draft]{book}

\usepackage{booktabs}

\usepackage{geometry}

\usepackage[toc]{glossaries}
\makeglossaries
\include{glossary}

\usepackage{listings}
\lstset{language=c}

\usepackage[round]{natbib}
\bibliographystyle{plainnat}

\usepackage{tabu}

\usepackage{tikz}

\begin{document}

\frontmatter

\title{Improving the EMS Library}
\author{Luke Bowden \& Callum O'Brien\\
    Exeter Mathematics School}
\date{\today}
\maketitle

\tableofcontents

\mainmatter

\chapter{Details and Context}

\section{Description of the Current System}

Exeter Mathematics School's library contains, as one might expect, books. Some
of the books are available to check out of the library, whereas others are not;
currently, this is communicated by stickers on the books with a grey sticker on
the spine of a book meaning one is not to take that book out of the library.
Other colour stickers of books' spines mean one can check them out.

When a student checks out a book, they find the book they are checking out in a
large log book containing all the books in the library wherein each book is
alotted a page. They write their name on the page, along with the current date.
Upon returning the book, they find the entry in the log book corresponding to
its checking out and add the date they returned it. If one wishes to find out
who has a book or, indeed, whether a book is currently in the library (without
visually searching the shelves), one must read through this log book, find the
lastest entry regarding the book one wishes to know about and see who checked it
out and/or whether the book has been returned.

\section{Inefficiencies Arising from the Current System}

Under the current system, students checking a book in or out are required to
manually search a reasonably large document (the log book) to find the page for
the book and then write their name and the date. This can take a long time and
is labourious for the student.

Additionally, there exists no means by which someone can remotely search the
books in the library to determine which ones are currently being borrowed or
whether the library has a book at all meaning that if a person wants to know
these data, they must physically go to the library. Even then, searching is
completely manual, consisting of finding the right pages in the log book and
checking whether each entry has a return date. This process is slow and
inconvenient.

A third issue with the current system is that is a student fails to notice that
a book has a grey sticker on its spine and proceeds to attempt to record their
borrowing of it, they may spend a long time searching for the book in the log
book before realising that that book should not be removed from the library. 

\section{Potential Solutions to Current Inefficiencies}

\section{Appraisal of Potential Solutions}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Design}

\section{Overall System Design}

The proposed system involves (as well as the obvious) a daemon, a database and
an NFC reader. Upon checking out a book, a student will touch both the book and
their identification card to an NFC reader device. This will invoke the daemon
which will query the Book and Student tables in the database for the UIDs of the
book and the student. After these data have been retrieved, the daemon will
query the database again, this time concerning the BookStudent table; the daemon
requests the UIDs of any BookStudent records whose BookID and StudentID
attributes are the recently retrieved UIDs and whose pending attribute is True.
This query will return either nothing or a single UID. If no UID is received,
the daemon will create a new record in the BookStudent table. This record will
have;\begin{itemize}

    \item BookID of the Book's UID

    \item StudentID of the Student's UID

    \item OutTime of the current time

    \item InTime of NULL

    \item Pending of True

\end{itemize} If a UID is received, the record with that UID is updated to
have;\begin{itemize}

    \item InTime of the current time

    \item Pending of False

\end{itemize}

\section{Entity Relationships \& Database Structure}

The database must encapsulate two entities, Book and Student, the Book entity
being an abstraction of a book in the EMS library and the Student entity being
an abstraction of a student attending EMS. The Book entity must contain all
information one might wish to identify a book by; its author, isbn, subject and
title. However, each instance of this entity must be unique and so a fifth
attribute, a UID, is required. The Student entity has attributes name and UID.

\begin{table}[h]

    \centering

    \begin{tabu} to 0.7\linewidth {lXX}

        \toprule

        Table       & Feild     & Type   \\

        \midrule

        Book        & Author    & Int    \\
                    & UID       & Int    \\
                    & ISBN      & String \\
                    & Subject   & String \\
                    & Title     & String \\
        
        BookStudent & BookID    & Int    \\
                    & InTime    & Date   \\
                    & OutTime   & Date   \\
                    & Pending   & Bool   \\
                    & StudentID & Int    \\
                    & UID       & Int    \\
        Student     & Name      & String \\
                    & UID       & Int    \\
        
        \bottomrule

    \end{tabu}

    \caption[Data Dictionary]{Tables and the fields they contain}

\end{table}

A single Student may take out many Books and a single Book may be taken out by
many Students, thus these entities have a many-to-many relationship. In order to
fully encapsulate these entities in a relational database we must normalise this
relationship, creating a third entity; BookStudent. A BookStudent record will be
created for every time a Student takes out a Book. This effects a one-to-many
relationship between Book and BookStudent and a many-to-one relationship between
BookStudent and Student (see figure 2.3).

\begin{figure}[h]

    \centering

    \begin{tikzpicture}

        % Book
        \draw (00.00,00.00) rectangle (03.00,01.00);
        \draw (01.50,00.50) node [text width=3cm, text centered] {Book};

        % Student
        \draw (05.00,00.00) rectangle (08.00,01.00);
        \draw (06.50,00.50) node [text width=3cm, text centered] {Student};

        % Book >-< Student
        \draw (03.00,00.50) -- (05.00,00.50);
        \draw (03.20,00.50) -- (03.00,00.70);
        \draw (03.20,00.50) -- (03.00,00.30);
        \draw (04.80,00.50) -- (05.00,00.70);
        \draw (04.80,00.50) -- (05.00,00.30);

    \end{tikzpicture}

    \caption[Unnormalised table structure]{The table structure of the database
    before normalisation.}

\end{figure}

\begin{figure}[h]

    \centering

    \begin{tikzpicture}

        % Book
        \draw (00.00,00.00) rectangle (03.00,01.00);
        \draw (01.50,00.50) node [text width=3cm, text centered] {Book};

        % BookStudent
        \draw (05.00,00.00) rectangle (08.00,01.00);
        \draw (06.50,00.50) node [text width=3cm, text centered] {BookStudent};

        % Student
        \draw (10.00,00.00) rectangle (13.00,01.00);
        \draw (11.50,00.50) node [text width=3cm, text centered] {Student};
       
        % Book -< BookStudent
        \draw (03.00,00.50) -- (5.00,0.50);
        \draw (04.80,00.50) -- (5.00,0.70);
        \draw (04.80,00.50) -- (5.00,0.30);

        % Student -< BookStudent
        \draw (08.00,00.50) -- (10.00,00.50);
        \draw (08.20,00.50) -- (08.00,00.70);
        \draw (08.20,00.50) -- (08.00,00.30);

    \end{tikzpicture}
    
    \caption[Normalised table structure]{The table structure of the database
    after normalisation.}

\end{figure}

\section{User Interface}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Implementation}

\section{Discussion of Language}

\section{Discussion of Platform}

\section{Issues and Resolutions}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Testing}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Evaluation}

\section{Assessment of Features}

\section{Known Bugs}

\appendix

\chapter{Source Code}

\backmatter

\listoffigures

\listoftables

\bibliography{emc}

\printglossaries

\end{document}

